---

date: "11/7/2021"
output: html_document
---

```{r libraries}
rm(list=ls())
library(readxl)
library(Hmisc)
library(MASS)
library(caret)
library(dplyr)
```

#### **Question 1: Has the online community increased user revenue? (2 points)**

```{r Question 1}

## Setting working directory
setwd("C:\\Users\\mahen\\OneDrive - University of California, Davis\\Desktop\\School\\BAX 401 Fall - Information, Insight and Impact\\Class 6\\HW3\\")

## Loading dateset
onemonth_data<-read_excel("Assignment3HW3_Data.xlsx",sheet=2)

## Stacking
onemonth_data_before <- onemonth_data %>% select(`Month Before`,`Joined?`)
onemonth_data_before$treated <- 0
colnames(onemonth_data_before)[1] <- "value"

onemonth_data_after <- onemonth_data %>% select(`Month After`,`Joined?`)
onemonth_data_after$treated <- 1
colnames(onemonth_data_after)[1] <- "value"

data <- rbind(onemonth_data_before,onemonth_data_after)
data$did <- data$`Joined?`*data$treated

## Diff in Diff model
model <- lm(data$value ~ data$`Joined?` + data$treated + data$did)

## Summary
summary(model)

```

#####  The coefficient for ‘did’ is the differences-in-differences estimator. The effect is significant at 5% with the treatment having a positive effect. So we can say that revenue has increased with online community

##### On an average the revenue is incresed by 29.018 dollars


#### **Question 2: Has the online community led to increased retention? (2 points)**

```{r Question 2}

sixmonth_data<-read_excel("Assignment3HW3_Data.xlsx",sheet=3)

#Model Fitting
sixlogit<-glm(`Churned at 3 months after launch of the online community` ~ 
              `Customer Age with Firm at time of launching the online community` + 
              `Joined?` +
              `Average Spend Last 3 months of Life with the firm`,data=sixmonth_data,family=binomial(link="logit"))

#coefficients
summary(sixlogit) 

#Confidence Intervals
confint(sixlogit) 

## AIC
AIC(sixlogit)

## Calculating retention probability
preddata<-with(sixmonth_data,data.frame(`Customer ID`,`Joined?`,
                                        `Customer Age with Firm at time of launching the online community`,
                                        `Churned at 3 months after launch of the online community`,
                                   `Average Spend Last 3 months of Life with the firm`))
colnames(preddata) <- colnames(sixmonth_data)
preddata$`Churned at 3 months after launch of the online community` <- NULL
probchurn<-predict(sixlogit,newdata=preddata,type="response")
predchurn<-ifelse(probchurn > 0.5, 1,0)
missclass<-predchurn!=sixmonth_data$`Churned at 3 months after launch of the online community`
misclasserror<-mean(predchurn!=sixmonth_data$`Churned at 3 months after launch of the online community`)
print(paste('Accuracy',1-misclasserror))

confMat2<-confusionMatrix(data = as.factor(predchurn),reference = as.factor(sixmonth_data$`Churned at 3 months after launch of the online community`),positive = "1")
confMat2

## Creating final data set with churn probability
finaldata<-cbind(sixmonth_data,probchurn,predchurn,missclass)

## Creating retention Probability
finaldata$retention <- 1-finaldata$probchurn

## Retention model
retention_model <- lm(finaldata$retention ~ finaldata$`Joined?` + finaldata$`Average Spend Last 3 months of Life with the firm` + finaldata$`Customer Age with Firm at time of launching the online community`)

summary(retention_model)
```
#### All the coefficients are significant. We can see that average retention is reduced by 21.3% keeping average spend and customer age constant.


#### **Question 3: Has the online community led to an increase in CLV? (Assume a margin of 50% of customer spend) (2 points)**

```{r Question 3}

## CLV Calculation with 10% discount
finaldata$CLV <- (finaldata$`Average Spend Last 3 months of Life with the firm`/2)* (1.1/(1.1-finaldata$retention))

## CLV Model
CLV_model <- lm(finaldata$CLV ~ finaldata$`Joined?` + finaldata$`Average Spend Last 3 months of Life with the firm` + finaldata$`Customer Age with Firm at time of launching the online community`)

## Model Summary
summary(CLV_model)

```
#### All the coefficients are significant. We can see that average CLV is reduced by 20.98 dollars keeping average spend and customer age constant.

### ADDING Campaign/Organic variable into the model

```{r}

sixmonth_data<-read_excel("Assignment3HW3_Data.xlsx",sheet=4)
colnames(sixmonth_data)
#Model Fitting
sixlogit<-glm(`Churned at 3 months` ~ `Campaign/Organic` +
                `Customer Age with Firm at time of launching the online community` + 
                `Joined?` +
                `Average Spend Last 3 months of Life with the firm`,data=sixmonth_data,family=binomial(link="logit"))

#coefficients
summary(sixlogit) 

#Confidence Intervals
confint(sixlogit) 

#exponentiated coefficients
#exp(mylogit$coefficients)

#exponentiated confidence intervals
#exp(confint(mylogit))

AIC(sixlogit)

preddata<-with(sixmonth_data,data.frame(`Customer ID`,`Campaign/Organic`,`Joined?`,
                                        `Customer Age with Firm at time of launching the online community`,
                                        `Churned at 3 months`,
                                        `Average Spend Last 3 months of Life with the firm`))
colnames(preddata) <- c("Customer ID","Campaign/Organic","Joined?",
                        "Customer Age with Firm at time of launching the online community",
                        "Churned at 3 months",                                            
                        "Average Spend Last 3 months of Life with the firm")
preddata$`Churned at 3 months` <- NULL
probchurn<-predict(sixlogit,newdata=preddata,type="response")
predchurn<-ifelse(probchurn > 0.5, 1,0)
missclass<-predchurn!=sixmonth_data$`Churned at 3 months`
misclasserror<-mean(predchurn!=sixmonth_data$`Churned at 3 months`)
print(paste('Accuracy',1-misclasserror))

confMat2<-confusionMatrix(data = as.factor(predchurn),reference = as.factor(sixmonth_data$`Churned at 3 months`),positive = "1")
confMat2

## Final data set with probability of churn
finaldata<-cbind(sixmonth_data,probchurn,predchurn,missclass)

## Creating Retention Column
finaldata$retention <- 1-finaldata$probchurn

## Creating CLV Column with 10% discount
finaldata$CLV <- (finaldata$`Average Spend Last 3 months of Life with the firm`/2)*(1.1/(1.1-finaldata$retention))

```

#### Revenue

```{r}
## revenue model
revenue_model <- lm(finaldata$`Average Spend Last 3 months of Life with the firm` ~ finaldata$`Campaign/Organic` + finaldata$`Joined?` + finaldata$`Customer Age with Firm at time of launching the online community`)
summary(revenue_model)
```

#### Retention

```{r}
## Retenrion Model
retention_model <- lm(finaldata$retention ~ finaldata$`Campaign/Organic` + finaldata$`Joined?` + finaldata$`Average Spend Last 3 months of Life with the firm` + finaldata$`Customer Age with Firm at time of launching the online community`)
summary(retention_model)
```

#### All the coefficients are significant. We can see that the probability of retention is approximately 4.1% less when compared to an organically acquired customer keeping Customer Age and Average Spend Constant


#### CLV

```{r}
## CLV Model
clv_model <- lm(finaldata$CLV ~ finaldata$`Campaign/Organic` + finaldata$`Joined?` + finaldata$`Average Spend Last 3 months of Life with the firm` + finaldata$`Customer Age with Firm at time of launching the online community`)
summary(clv_model)

```


#### All the coefficients are significant. We can see that CLV of the customer, when acquired using Campaign,is on an average 4.02$ less than the customer acquired organically keeping Customer Age and Average Spend Constant

